Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-09-02 write-up/covid-writeup.tex
Update covid-writeup.tex

 Unfortunately, the first term of the doubly robust estimator cannot be computed as covariate information is not collected on the entire population.  Here, we suppose the same asymptotic regime as in Section~\ref{section:asymptotics} and use the probability sample at the time~$t \in \{t_l^\prime\}$ to estimate this term:
 $$
 \frac{1}{\sum_{j=1}^N \tilde I_{j,t} \tilde W_{j,t}} \sum_{j=1}^N  \tilde I_{j,t} \tilde W_{j,t} \hat \mu_{t} (X_{j,t}) + \frac{1}{\sum_{j=1}^N I_{j,t} w (X_{j,t})} \sum_{j=1}^N I_{j,t} w(X_{j,t}) \left( \frac{Y_{j,t} - FP}{1 - FP - FN} - \hat \mu_t(X_{j,t}) \right).
 $$
 Assuming the selection propensity model is correctly specified, then under the design of the probability sample and design of the subsample from the nonprobability sample, Lemma~\ref{lemma:dr} shows that the doubly robust estimator is consistent and calculates the estimator's variance. See Appendix~\ref{app:asympderivations} for additional details.

>>>>

 Unfortunately, the first term of the doubly robust estimator cannot be computed as covariate information is not collected on the entire population.  Here, we suppose the same asymptotic regime as in Section~\ref{section:asymptotics} and use the probability sample at the time~$t \in \{t_l^\prime\}$ to estimate this term:
 $$
 \frac{1}{\sum_{j=1}^N \tilde I_{j,t} \tilde W_{j,t}} \sum_{j=1}^N  \tilde I_{j,t} \tilde W_{j,t} \hat \mu_{t} (X_{j,t}) + \frac{1}{\sum_{j=1}^N I_{j,t} w (X_{j,t})} \sum_{j=1}^N I_{j,t} w(X_{j,t}) \left( \frac{Y_{j,t} - FP}{1 - FP - FN} - \hat \mu_t(X_{j,t}) \right).
 $$
 Assuming correct selection propensity model specification, then under the probability sample design and nonprobability sample design, Lemma~\ref{lemma:dr} shows that the doubly robust estimator is consistent and calculates the estimator's variance. See Appendix~\ref{app:asympderivations} for additional details.
